Results

### 2019-03-10 analysis/02_analysis.Rmd
Dynamically include all reported values!
\(•◡•)/ R Markdown! \(•◡•)/

@@

>>>>

# Save combined table for later use in manuscript
tbl_likely_tidy %>% 
  left_join(tbl_likely_probs, by = "title") %>% 
  saveRDS(here("data", "derived_data", "results_models_likely.rds"))

@@

# Save combined table for later use in manuscript
tbl_amounts_tidy %>% 
  left_join(tbl_amounts_probs, by = "title") %>% 
  saveRDS(here("data", "derived_data", "results_models_amount.rds"))
